---
title: "Problem Set 1"
author: "Your Name"
date: "Add Date"
format: pdf
---


## Question 1

#### 1a) Put question 1a text here.

Put answer here. You can format your text as *italic* and **bold**.

New paragraphs go on their own line, separated by an empty line.

 - first
 - second item
 - third
 




#### 1b) Put question 1b text here.

Inline math goes between dollar signs (e.g., $\beta$).

Centered math goes between double dollar signs:

$$
\hat{\beta} = (X'X)^{-1}X'y 
$$

You can align math using the `align` or `flalign` latex-style environments. Alignment is based on the ampersand, newlines are created with a double backslash, and equation numbering is controlled by the asterisk:

\begin{align*}
  c^2 
  &= a^2 + b^2 \\
  &= (a \times a) + (b \times b)
\end{align*}




## Question 2

#### 2a) Put question 2a text here

You can write inline code that gets evaluated like so: `r x=3; x^2`. 

Or you can write inline code that doesn't get evaluated: `x^2`.

You can write code between triple ticks and control evaluation with the `eval` option. Evaluated code will print the results of evaluation into the rendered version of this document.

```{r, echo=TRUE}
library(data.table)
data(mtcars)
setDT(mtcars)
y <- 7
y^2
```

```{r, fig.height=3, fig.width=5}
plot(1:10, (1:10)^2, pch=20, main="My Plot", xlab="X", ylab="Y")
```


#### 2b) Put question 2b text here

All of this information (and much more) is available on the Quarto [website](https://quarto.org/docs/guide/).





## Challenge Question

The two chunks below are supposed to report the average fuel economy of
**4-cylinder** cars. This document renders with no error and no warning, and the
sentence underneath them prints a number that is simply wrong.

```{r}
data(mtcars)
avg_mpg <- mean(mtcars$mpg)
```

```{r}
#| eval: false
mtcars <- subset(mtcars, cyl == 4)
avg_mpg <- mean(mtcars$mpg)
```

The average mpg of 4-cylinder cars is `r round(avg_mpg, 2)`.

a)  Render the document. What number appears in the sentence above, and what
    should it be?

b)  Which chunk option caused it? Explain why nothing in the rendered output
    hints that a chunk was skipped.

c)  Running these chunks one at a time in the console will not reveal the
    problem, and neither will re-rendering. Explain why, then name the habit
    that does catch it.

d)  Fix it twice. First by changing the chunk option. Then a second way, by
    rewriting the sentence so that the prose cannot drift out of sync with the
    data even if someone edits the chunks later.

e)  This is the failure mode that makes a rendered report dangerous rather than
    merely wrong: the document looks finished. In two sentences, describe what
    you would check before sending a rendered PDF to someone who will act on it.
