---
title: "Problem Set 1"
author: "Your Name"
date: "Add Date"
format: pdf
---


## Question 1

#### 1a) Put question 1a text here.

Put answer here. You can format your text as *italic* and **bold**.

New paragraphs go on their own line, separated by an empty line.

 - first
 - second item
 - third
 




#### 1b) Put question 1b text here.

Inline math goes between dollar signs (e.g., $\beta$).

Centered math goes between double dollar signs:

$$
\hat{\beta} = (X'X)^{-1}X'y 
$$

You can align math using the `align` or `flalign` latex-style environments. Alignment is based on the ampersand, newlines are created with a double backslash, and equation numbering is controlled by the asterisk:

\begin{align*}
  c^2 
  &= a^2 + b^2 \\
  &= (a \times a) + (b \times b)
\end{align*}




## Question 2

#### 2a) Put question 2a text here

You can write inline code that gets evaluated like so: `r x=3; x^2`. 

Or you can write inline code that doesn't get evaluated: `x^2`.

You can write code between triple ticks and control evaluation with the `eval` option. Evaluated code will print the results of evaluation into the rendered version of this document.

```{r, echo=TRUE}
library(data.table)
data(mtcars)
setDT(mtcars)
y <- 7
y^2
```

```{r, fig.height=3, fig.width=5}
plot(1:10, (1:10)^2, pch=20, main="My Plot", xlab="X", ylab="Y")
```


#### 2b) Put question 2b text here

All of this information (and much more) is available on the Quarto [website](https://quarto.org/docs/guide/).





